### 2019-09-22 papers/journal/2019_ACTA_Rebuttal_Rd2.txt

We would like to thank the reviewers for their very detailed 
and helpful comments. 
In the following, we elaborate on how we addressed the feedback 
in the revised version of our paper.

% Reviewer 1:
  >> My comments and concerns have been addressed in detail. 
    Thank you.
  Authors response: Thank you for your valuable comments.

% Reviewer 3:

  >> I believe that most issues highlighted previously have been 
  addressed adequately. In particular, the structure of the 
  revised manuscript has been improved significantly. 
  I still found the paper challenging to read, but this is 
  largely due to the complexity of the biological system and 
  the necessary encoding details presented in the manuscript.

@@

  Authors response: Thank you for this feedback. As we are trying 
  to reach an interdisciplinary audience we are forced to balance 
  to some extent the biological detail with the technical discussions. 
  We appreciate the feedback from the reviewers, which has helped us 
  improve readability.

  >> One point that I think requires further attention is the 
  motivation for using connectedness and the explanation of 
  this property, which is at the core of the proposed approach. 
  I did not find the additional explanations provided in the 
  response and the revised manuscript sufficient. Simply stating 
  that "The graph k-connectedness furnishes precisely" a test to 
  determine if information is missing from the model.

  Authors response: We have removed the word "precisely", 
  which the Reviewer has correctly pointed out is too strong. 
  We have replaced this by the sentence 
  "It has been shown that graph $k$-connectedness furnishes one such test".

  >> "If the data […] does not have a certain degree of 
  connectivity, this implies that some biological data has been 
  missed" does not  justify connectedness as a fundamental and 
  required biological  property that all valid models should respect. 
  The intuition of connectedness as a robustness property provided 
  elsewhere in the  manuscript helps but it is still not clear what 
  evidence supports  the fact that VTSs are indeed robust. In addition, 
  the problem as  formulated does not seem to seek the most robust 
  networks as  explained in the following.

@@

  Author response: We have added several paragraphs 
  to motivate our focus on k-edge-connectedness:

  "The informativeness and usefulness of using $k$-connectedness 
  is motivated by the following example. ... In summary, the higher 
  the edge-connectedness of a measured VTS graph, the more of the 
  underlying biological constraints can be satisfied by appropriately 
  placing SNAREs on each node and edge."

  >> Finally, it is not clear why the goal is to find the minimum 
  graph connectivity, given that larger connectivity corresponds 
  to a more robust network. I was expecting an approach involving 
  incrementing k to find the smallest value that makes the formula 
  unsatisfiable, thus identifying the maximum graph connectedness 
  possible for a given VTS with all other constraints being satisfied. 
  However, to the best of my understanding, this is not what the paper 
  is currently proposing, or else further clarifications are needed.

@@

  Author response: We apologise for the confusing structure 
  of our text. To clarify this point we have added a new paragraph:

  "It is perhaps counter-intuitive that, beyond a certain degree 
  of edge-connectedness, any VTS graph can be implemented as a 
  biological system. This is because we have not placed any 
  constraints on the number of distinct SNAREs and other trafficking 
  molecules a cell contains. In practice there is an upper bound on the 
  number of molecules a cell can genetically encode. This question 
  ("What is the maximum edge-connectedness possible given a 
  certain number of SNAREs?") is complementary to the question we 
  have asked here ("What is the minimum edge-connectedness possible 
  given any number of SNARES operating under certain physical constraints?")."

  >> I also found the formulation of the main problems with 
  respect to connectedness somewhat confusing. For example, 
  in Sec. 5.1.1 and Sec. 5.1.2 the problems are formulated   
  as a search for VTS G such that G is not k-connected. 
  Yet, Sec. 5.1 specifies that "In case the formula is 
  satisfiable the procedure terminates and we report the 
  value of k", which seems contradictory.

  Authors response: In Sec. 5 we try to give a high-level 
  specification of the procedure, followed by a formal search 
  statement from a perspective of an efficient implementation. 
  This difference was only hinted but not explicitly stated. 
  We have now rewritten the parts of the text to address the 
  distinction between high-level overview and the implementation.
  We have also removed the specific search problems (as suggested 
  by Reviewer #3 in the first revision) for further apparent 
  accessibility of the subject matter. 
  The use of "k" in the 6.1.6 k-connectivity constraints, 
  is overloaded. It just specifies how we encode a graph 
  that is not k-connected.

  >> Another point that should be revised further is around 
    clarifying the contributions of this paper. The response 
    document summarizes nicely that, together with additional 
    QBF encoding, "this paper brings together all the results 
    with extended experiments and more detailed expositions for 
    the benefit of both biological and computation community." 
    However, I did not find a similar concise statement of the 
    contributions in the text. In addition, some of the stated 
    advances over previous approaches seem incremental and minor. 
    For example, for the previous CBMC-based method it is stated 
    that "...the scalability of the method was insufficient. 
    The tool was able to handle the system with just eight 
    compartments". Yet, we learn that "A typical eukaryotic 
    cell contains 9 organelles" and even one of the methods 
    presented in this paper fails for some of the experimental 
    evaluations with 7 or more compartments. The contributions 
    of this work, perhaps in the integration and evaluation of
    several methods reported previously, should be stated clearly 
    and accurately in the main text.

@@

  Authors response: We clarified the concerns of the reviewers and 
  clearly stated in the Sec 1. Introduction that the CBMC method 
  does not scale and the direct encoding does. 
  We have also stated that the key purpose of this paper 
  is one unified exposition of our work.

  >> A final minor point is about the use of "Synthesis" as 
    an encoding in Fig 4 and the relevant explanations. 
    Since the other problems list verification techniques 
    and solvers (e.g. BMC, SMT, QBF) and no novel synthesis 
    algorithms were developed for this problem, it would be 
    more appropriate to specify QBF as the encoding used for 
    the "VTS synthesis" problem.

@@

% Reviewer 4:

  >> Point 6 on page 3 is the same as point 4.

  Authors response: We thank the reviewer for pointing 
  this out. The two points were indeed duplicates. We 
  have now removed point 6.

  >> I would argue still that the biological section has 
    unnecessary detail and could be simplified further.

@@

  Authors response: We acknowledge that in the paper, 
  we only deal explicitly with SNARE proteins. Although 
  it is not required for an understanding of the work, 
  we feel a glimpse of the kinds of processes involved 
  in vesicle traffic, and its molecular machinery might 
  help the reader appreciate why we have built our model 
  in this particular way.

  >> That the steady-state condition corresponds to the 
    biological meaning of homeostasis is repeated. This 
    only needs to be mentioned once.

@@

  Authors response: We now state the equivalence of our 
  steady state condition and homeostasis of compartments
  only in section 2.3.2.

  >> There is overlap in the 3rd and 6th paragraphs of 
    the 'Related Work' section, which refer to the use 
    of SAT/SMT in GRNs.

### 2019-09-22 papers/journal/encoding.tex
Added the connectivity fix
Minor updates in k-coonectivity

\subsubsection{$k$-connectivity constraints}
To check whether $k$-connected is a necessary condition, we remove (drop) $k-1$ edges from the graph and if it
disconnects the graph, and we get an assignment. We have a graph that is not  $k$-connected.
%
Constraints \texttt{Fail}(d,k), \texttt{FReach}(d,r') and \texttt{Connected}(r')
encode the relevant constraints for reachability
in the modified VTS. 
%
The following constraints encode that only
existing edges can be dropped and exactly $k-1$ edges are dropped.
\begin{align*}
\texttt{Fail}(d,k) = & 
\bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \land 
\sum_{i,j,q} d_{i,j,q} = k-1\\
\end{align*}

%We have used logarithmic bitwise encoding to express the cardinality constraint that exactly $k-1$ edges are dropped. 
%To encode exactly $k$ edges are dropped we need to express cardinality constraint to allow exactly $k$ edges to be true from set of all present edges $e$. 
%
We need to define reachability in the modified VTS, therefore we use
a new variable $r'_{i,j}$ to encode reachability from $i$ to $j$.
In the following constraint, we encode $r'_{i,j}$ is true if there is an
edge $(i,\_,j)$ and it is not dropped, or there is a node
$i^{\prime}$ such that, there is an edge $(i,\_,i^{\prime})$ which is
not dropped and $r'_{i',j}$ is true.
\begin{align*}
\texttt{FReach}(d,r') = &  \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}  
\end{align*}
Since we search for disconnected modified VTS,
the following constraint encodes that there are 
unreachable pair of nodes in the underlying undirected graph.
% nodes such that
% there is no path between them .
\begin{align*}
   \texttt{Connected}(r')  = & \bigvee\limits_{i,j} \neg (r^{\prime}_{i,j} \lor r^{\prime}_{j,i})
\end{align*}
We define $\texttt{Connected}(k)$ that says graph is not k-connected.
\begin{align*}
\texttt{Connected}(k) = \texttt{Fail}(d,k) \land \texttt{FReach}(d,r') \land \texttt{Connected}(r') 
% \\
% \texttt{Disconnected}(k) = & \exists d.\;
%         (\texttt{Drop}(d,k) \land \exists r'.\;\texttt{ReachAbove}(d,r')
%                               \land \lnot \texttt{Connected}(r'))
\end{align*}
% We can go down or up using -C \_ option.  \newline

>>>>

\subsubsection{$k$-connectivity constraints}
%To check whether $k$-connected is a necessary condition, 
We remove (drop) $k-1$ edges from the graph and if it
disconnects the graph, and we get an assignment. We have a graph that is not  $k$-connected.
%
Constraints \texttt{Fail}(d,k), \texttt{FReach}(d,r') and \texttt{Connected}(r')
encode the relevant constraints for reachability
in the modified VTS. 
%
The following constraints encode that only
existing edges can be dropped and exactly $k-1$ edges are dropped.
\begin{align*}
\texttt{Fail}(d,k) = & 
\bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \land 
\sum_{i,j,q} d_{i,j,q} = k-1\\
\end{align*}

%We have used logarithmic bitwise encoding to express the cardinality constraint that exactly $k-1$ edges are dropped. 
%To encode exactly $k$ edges are dropped we need to express cardinality constraint to allow exactly $k$ edges to be true from set of all present edges $e$. 
%
We need to define reachability in the modified VTS, therefore we use
a new variable $r'_{i,j}$ to encode reachability from $i$ to $j$.
In the following constraint, we encode $r'_{i,j}$ is true if there is an
edge $(i,\_,j)$ and it is not dropped, or there is a node
$i^{\prime}$ such that, there is an edge $(i,\_,i^{\prime})$ which is
not dropped and $r'_{i',j}$ is true.
\begin{align*}
\texttt{FReach}(d,r') = &  \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}  
\end{align*}
Since we search for disconnected modified VTS,
the following constraint encodes that there are 
unreachable pair of nodes in the underlying undirected graph.
% nodes such that
% there is no path between them .
\begin{align*}
   \texttt{Connected}(r')  = & \bigvee\limits_{i,j} \neg (r^{\prime}_{i,j} \lor r^{\prime}_{j,i})
\end{align*}
We define $\texttt{Connected}(k)$ that says graph is not $k$-connected.
\begin{align*}
\texttt{Connected}(k) = \texttt{Fail}(d,k) \land \texttt{FReach}(d,r') \land \texttt{Connected}(r') 
% \\
% \texttt{Disconnected}(k) = & \exists d.\;
%         (\texttt{Drop}(d,k) \land \exists r'.\;\texttt{ReachAbove}(d,r')
%                               \land \lnot \texttt{Connected}(r'))
\end{align*}
% We can go down or up using -C \_ option.  \newline

### 2019-09-22 papers/journal/problem.tex
Updated the Spec text
Minor updates in k-coonectivity

The specification of the $k$-connectedness property is challenging as it requires reasoning about all possible $k - 1$ edge removals. 
%
So instead of checking for the graph to be $k$-connected, the encoding (and the implementation) checks whether the graph is not $k+1$-connected.
%
Note that this check is sufficient as we are starting from smallest $k$ ($k = 1$) and subsequently incrementing it by one.     
% Used E as edge and L_e L_n as label for node and the edge,

@@

For the efficient implementation of the specification instead of checking the satisfiability of the formula, we check whether the negation of the formula is unsatisfiable. 
%
That is to conclude that a given $k$-connectedness is not a universal condition we search for a $k$-connected graph that has no satisfying assignment to all the rules of the system.
%
In case no such graph exists for a specific $k$ we reported the corresponding $k$.
%%\ankit{This is a dummy template. need a rewrite.} 
%\subsubsection{$\fqbf$ search problem.} For a given $k$, size $\nu$, and molecule number $\mu$, we are searching for a $k$-connected graph such that there is no assignment that makes it a well-structured, stable, and well-fused VTS $G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ with $|\nodes| = \nu$, $|\mols| = \mu$.

>>>>

The implementation of the $k$-connectedness property is challenging as it requires reasoning about all possible $k - 1$ edge removals. 
%
So instead of checking for the graph to be $k$-connected, the encoding (and the implementation) checks whether the graph is not $k+1$-connected.
%
Note that this check is sufficient as we are starting from smallest $k$ ($k = 1$) and subsequently incrementing it by one.     
% Used E as edge and L_e L_n as label for node and the edge,

@@

For the efficient implementation of the specification instead of checking the satisfiability of the formula, we check whether the negation of the formula is unsatisfiable. 
%
That is to conclude that a given $k$-connectedness is not a universal condition we search for a $k$-connected graph that has no satisfying assignment to all the rules of the system.
%
%In case no such graph exists for a specific $k$ we report the $k$.
%%\ankit{This is a dummy template. need a rewrite.} 
%\subsubsection{$\fqbf$ search problem.} For a given $k$, size $\nu$, and molecule number $\mu$, we are searching for a $k$-connected graph such that there is no assignment that makes it a well-structured, stable, and well-fused VTS $G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ with $|\nodes| = \nu$, $|\mols| = \mu$.
